Structured Versus Decorated Cospans

### 2020-11-23 cospans.tex
Shortening Appendix A.3

An `open system' is any sort of system that can interact with the outside world.  Experience has shown that open systems are nicely modeled using cospans \cite{CourserThesis, FongThesis, PollardThesis}. A cospan in some category $\A$ is a diagram of this form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$m$};
\node (C) at (2,0) {$b$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
We call $m$ the \define{apex}, $a$ and $b$ the \define{feet}, and $i$ and $o$ the \define{legs} of the cospan.   The apex describes the system itself.  The feet describe `interfaces'  through which the system can interact with the outside world.  The legs describe how the interfaces are included in the system.   If the category $\A$ has finite colimits, we can compose cospans using pushouts: this describes the operation of attaching two open systems together in series by identifying one interface of the first with one of the second.  We can also `tensor' cospans using coproducts: this describes setting open systems side by side, in parallel.  Via these operations we obtain a symmetric monoidal double category
%%%Christina: add the notation bb{C}sp(A) since it will be central to what follows?
with cospans in $\A$ as its horizontal 1-cells \cite{Courser,Niefield}.
%%% Christina: I would be inclined to first cite Niefield and then Courser due to the chronological order.

@@

@@

As a left adjoint, this induced $L$ preserves all colimits that exist between the finitely cocomplete categories $\A$ and $\inta F$, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{thm:SC}. Its objects and vertical morphisms are those of the category $\A$ (as for $F\lCsp$ earlier), whereas horizontal 1-cells are now cospans of the form $\cspn{L(a)}{(m,x)}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (\cref{def:GrothCat}). Explicitly, they consist of two pairs of morphisms 
%%% Not sure what v is in the above line unless you mean x?
%%% I mean an arbitrary object in the Grothendieck category. I just made it a pair to be clearer, is it OK? Erase these comments whenever you want.
\begin{equation}\label{eq:scsphor1cell}
 (a,\bot_a)\xrightarrow{\scalebox{0.7}{\(\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}\)}}(m,x)\xleftarrow{\scalebox{0.7}{\(\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}\)}}(b,\bot_b)
\end{equation}
with $x\in F(m)$; recall that the reindexing functors $F(i),F(o)$ preserve all finite colimits across the fibre categories.
Finally, the 2-morphisms of this double category in this context unravel as follows
\begin{equation}\label{eq:2morphismLCspintaF}
 \begin{tikzcd}[row sep=1in,column sep=1.7in,ampersand replacement=\&]
 (a,\bot_a)\ar[r,"{\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}}"]\ar[d,"{\begin{cases}f\maps a\to a' &\textrm{in }\A \\\chi_a\maps F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (m,x) \ar[d,"{\begin{cases}k\maps m\to m' &\textrm{in }\A \\ \tau\maps F(k)(x)\to x' &\textrm{in }F(m')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}}"']\ar[d,"{\begin{cases}g\maps b\to b' &\textrm{in }\A \\\chi_b\maps F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
 (a',\bot_{a'})\ar[r,"{\begin{cases}i'\maps a'\to m' &\textrm{in }\A \\!\maps F(i')(\bot_{a'})\to x' &\textrm{in }F(m')\end{cases}}"'] \& (m',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\maps b'\to m' &\textrm{in }\A \\!\maps F(o')(\bot_{b'})\to x' &\textrm{in }F(m')\end{cases}}"]
 \end{tikzcd}
\end{equation}
where the outside vertical legs come from the definition of $L$ on arrows \cref{eq:Lonarrows}. 
Explicitly, the above square commutativities translate to the conditions $k\circ i=i'\circ f$ and $k\circ o=o'\circ g$ in $\A$, and also to
\begin{gather}\label{eq:Grothcommutativity}
 F(k\circ i)(\bot_a)\cong Fk(Fi(\bot_a))\xrightarrow{Fk(!)}Fk(x)\xrightarrow{\tau}x'= \\
 F(i'\circ f)(\bot_a)\cong Fi'(Ff(\bot_a))\xrightarrow{Fi'(\chi_a)}Fi'(\bot_{a'})\xrightarrow{!}x'\nonumber
\end{gather}
in the fibre category $F(m')$, by composition in the Grothendieck category \cref{eq:compGrothcat}. Since both morphisms emanate from the mapped initial object in $F(m')$ under the finitely cocontinuous reindexing functors, they are the unique such into $x'$ therefore this gives no extra conditions; similarly for the equality including $o,o'$.

@@

%%% Is this biequivalnce symmetric monoidal? Mike says yes, but it follows from a result that he has yet to officially publish. It's a result of a paper he's currently working on with someone.
%%% Christina: Kenny, is the above comment still relevant? If not, feel free to erase!

@@

\subsection{Double categories}\label{sec:doublecats}
%%% Christina: Kenny, would you mind cleaning this section up to? I don't believe we need the full fledged definitions here by the way.

Before formally defining `pseudo double category', it is helpful to have the following picture in mind. A pseudo double category has 2-morphisms shaped like:

\[
\begin{tikzpicture}[scale=1]
\node (D) at (-4,0.5) {$A$};
\node (E) at (-2,0.5) {$B$};
\node (F) at (-4,-1) {$C$};
\node (A) at (-2,-1) {$D$};
\node (B) at (-3,-0.25) {$\Downarrow a$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above]{$M$}(E)
(E) edge node [right]{$g$}(A)
(D) edge node [left]{$f$}(F)
(F) edge node [above]{$N$} (A);
\end{tikzpicture}
\]
We call $A, B, C$ and $D$ \define{objects} or \define{0-cells}, $f$ and $g$ \define{vertical 1-morphisms}, $M$ and $N$ \define{horizontal 1-cells} and $a$ a \define{2-morphism}. Note that a vertical 1-morphism is a morphism between 0-cells and a 2-morphism is a morphism between horizontal 1-cells. %We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'???   Or should we put a ``tick'' in here?
We follow the notation of Shulman \cite{Shulman2008} with the following definitions.

@@

\end{center}
such that $S(\alpha), S(\lambda), S(\rho), T(\alpha), T(\lambda)$ and $T(\rho)$ are all identities and that the coherence axioms of a monoidal category are satisfied. Following the notation of Shulman, objects of $\lD_0$ are called \define{objects} or \define{0-cells}
%%% I'm tempted to delete 0-cells since we never use that term anywhere in any paper, but I do like the idea that "n+1 morphisms go between n cells".
%%% Christina: I am up for deletion of 0-cells
and morphisms of $\lD_0$ are called \define{vertical 1-morphisms}. Objects of $\lD_1$ are called \define{horizontal 1-cells} and morphisms of $\lD_1$ are called \define{2-morphisms}. The morphisms of $\lD_0$, which are vertical 1-morphisms, will be denoted $f \maps A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \maps A \to B$. Then a 2-morphism $a \maps M \to N$ of $\lD_1$ with $S(a)=f,T(a)=g$ would look like:
\[
\begin{tikzpicture}[scale=1]
\node (D) at (-4,0.5) {$A$};
\node (E) at (-2,0.5) {$B$};
\node (F) at (-4,-1) {$C$};
\node (A) at (-2,-1) {$D$};
\node (B) at (-3,-0.25) {$\Downarrow a$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above]{$M$}(E)
(E) edge node [right]{$g$}(A)
(D) edge node [left]{$f$}(F)
(F) edge node [above]{$N$} (A);
\end{tikzpicture}
\]
\end{defn}
A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}.

@@

%\begin{defn}
%Let $\lD$ be a pseudo double category. Then the $\textbf{horizontal bicategory}$ of $\lD$, which we denote as $H(\lD)$, is the bicategory consisting of objects of $\lD$, morphisms that are horizontal 1-cells of $\lD$ and 2-morphisms that are globular 2-morphisms of $\lD$.
%\end{defn}

\begin{defn}\label{def:doublefun}
Let $\lA$ and $\lB$ be double categories. A \define{(pseudo) double functor} is a functor $\lF \maps\lA\to \lB$ that takes items of $\lA$ to items of $\lB$ of the corresponding type, respecting vertical composition in the strict sense and the horizontal composition up to an assigned comparison $\phi$. This means that we have functors $\lF_0 \maps \lA_0 \to \lB_0$ and $\lF_1 \maps \lA_1 \to \lB_1$ such that the following equations are satisfied: 
\[   S \circ \lF_1 = \lF_0 \circ S, \qquad  T \circ \lF_1 = \lF_0 \circ T. \]
Sometimes for brevity we omit the subscripts and simply write $\lF$.

@@

 \[\xymatrix{
    (\lF(N_1) \odot \lF(N_{2})) \odot \lF(N_{3}) \ar[r]^{a'}\ar[d]_{\phi(N_1,N_{2}) \odot 1}
    & \lF(N_1) \odot (\lF(N_{2}) \odot \lF(N_{3})) \ar[d]^{1 \odot \phi(N_{2},N_{3})}\\
    \lF(N_1 \odot N_{2}) \odot \lF(N_{3}) \ar[d]_{\phi(N_1 \odot N_{2},N_{3})} &
    \lF(N_1) \odot \lF(N_{2} \odot N_{3}) \ar[d]^{\phi(N_1,N_{2} \odot N_{3})}\\
    \lF((N_1 \odot N_{2}) \odot N_{3})\ar[r]^{\lF(a)} &
    \lF(N_1 \odot (N_{2} \odot N_{3}))}\]
\end{enumerate}
We say the double functor $\lF$ is \define{strict} if the comparison constraints $\phi_a$ and $\phi_{N_1,N_2}$ are identities, \define{pseudo} if the comparison constraints are isomorphisms, and \define{oplax} if the comparison constraints go in the opposite direction.
\end{defn}

@@

%Following the notation of Shulman \cite{Shulman2010}, given a double category $\lA$, we write $_f \lA_g(M,N)$ for the set of 2-morphisms in $\lA$ of the form:
%\[
% \xymatrix@-.5pc{
%   A \ar[r]|{|}^{M}  \ar[d]_f \ar@{}[dr]|{\Downarrow a}&
%    B\ar[d]^g\\
%    C \ar[r]|{|}_N & D
%  }
%\]
We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively. Thus $_f \lA_g(M,N)$ denotes the set of 2-morphisms in $\lA$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.

@@

\begin{thm}
Let $\lA$ and $\lX$ be symmetric monoidal double categories and let $\lF \maps \lA \to \lX$ be a symmetric monoidal strong double functor. If $\lF$ is part of a double equivalence, then $\lF$ is in fact part of a symmetric monoidal double equivalence, and $\lA$ and $\lX$ are equivalent as symmetric monoidal double categories.
\end{thm}

\begin{proof} Where is this proved???  \end{proof}

@@

  A \textbf{monoidal double category} is a double category $\lD$ equipped with the following

@@

  Let $\lD$ be a double category and $f\maps A\to B$ a vertical

@@

	\end{tikzpicture}
	}
	%
	\raisebox{-0.5\height}{=}
	%
	\raisebox{-0.5\height}{
	\begin{tikzpicture}
	     \node (A0) at (0,2) {$A$};
	     \node (B0) at (1,2) {$A$};
		\node (C0) at (2,2) {$B$};
		\node (A) at (0,1) {$A$};
		\node (C) at (2,1) {$B$};
	%	\node (A') at (0,0) {$a$};
	%	\node (C') at (2,0) {$b$};
		%
		\path[->,font=\scriptsize,>=angle 90]
			(A0) edge node[above]{$U_A$} (B0)
			(B0) edge node[above]{$\hat{f}$} (C0)
			(A0) edge node[left]{$1$} (A)
			(C0) edge node[right]{$1$} (C)
		%	(A) edge node[left]{$1$} (A')
		%	(C) edge node[right]{$1$} (C')
			(A) edge node[below]{$\hat{f}$} (C);
		%	(A') edge node[below]{$\hat{f}$} (C');
		%
	%	\draw (0.5,.925) -- (0.5,1.075);
	%	\draw (0.5,-.075) -- (0.5,.075);
	%	\node () at (1,0.5) {\scriptsize{$\Downarrow 1$}};
		\node () at (1,1.4) {\scriptsize{$\Downarrow \rho_f$}};
	\end{tikzpicture}
	}
	\end{equation}
  A \textbf{conjoint} of $f$, denoted $\fchk \maps B\to A$, is a
  companion of $f$ in the double category $\lD^{h\cdot\mathrm{op}}$
  obtained by reversing the horizontal 1-cells, but not the vertical
  1-morphisms, of $\lD$.
\end{defn}
\noindent
%In a pseudo double category, the second equation above requires an insertion of unit isomorphisms to make sense due to horizontal composition only holding up to isomorphism.

@@

>>>>

An `open system' is any sort of system that can interact with the outside world.  Experience has shown that open systems are nicely modeled using cospans \cite{CourserThesis, FongThesis, PollardThesis}. A cospan in some category $\A$ is a diagram of this form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$m$};
\node (C) at (2,0) {$b$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
We call $m$ the \define{apex}, $a$ and $b$ the \define{feet}, and $i$ and $o$ the \define{legs} of the cospan.   The apex describes the system itself.  The feet describe `interfaces'  through which the system can interact with the outside world.  The legs describe how the interfaces are included in the system.   If the category $\A$ has finite colimits, we can compose cospans using pushouts: this describes the operation of attaching two open systems together in series by identifying one interface of the first with one of the second.  We can also `tensor' cospans using coproducts: this describes setting open systems side by side, in parallel.  Via these operations we obtain a symmetric monoidal double category
%%%Christina: add the notation bb{C}sp(A) since it will be central to what follows?
with cospans in $\A$ as its horizontal 1-cells \cite{Niefield}.
%%% Christina: I would be inclined to first cite Niefield and then Courser due to the chronological order.
%%% Kenny: I think when we \cite{...}, we list the references alphabetically, but let's just cite Niefield here and achieve both.

@@

%%% Kenny: \phi:1-->F(0), F(!):F(0)-->F(a), F(f):F(a)-->F(a')? Or did I make a mistake somewhere?

@@

As a left adjoint, this induced $L$ preserves all colimits that exist between the finitely cocomplete categories $\A$ and $\inta F$, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{thm:SC}. Its objects and vertical morphisms are those of the category $\A$ (as for $F\lCsp$ earlier), whereas horizontal 1-cells are now cospans of the form $\cspn{L(a)}{(m,x)}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (\cref{def:GrothCat}). Explicitly, they consist of two pairs of morphisms 
%%% Not sure what v is in the above line unless you mean x?
%%% I mean an arbitrary object in the Grothendieck category. I just made it a pair to be clearer, is it OK? Erase these comments whenever you want.
%%% Oh, gotchya'
\begin{equation}\label{eq:scsphor1cell}
 (a,\bot_a)\xrightarrow{\scalebox{0.7}{\(\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}\)}}(m,x)\xleftarrow{\scalebox{0.7}{\(\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}\)}}(b,\bot_b)
\end{equation}
with $x\in F(m)$; recall that the reindexing functors $F(i),F(o)$ preserve all finite colimits across the fibre categories.
Finally, the 2-morphisms of this double category in this context unravel as follows
\begin{equation}\label{eq:2morphismLCspintaF}
 \begin{tikzcd}[row sep=1in,column sep=1.7in,ampersand replacement=\&]
 (a,\bot_a)\ar[r,"{\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}}"]\ar[d,"{\begin{cases}f\maps a\to a' &\textrm{in }\A \\\chi_a\maps F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (m,x) \ar[d,"{\begin{cases}k\maps m\to m' &\textrm{in }\A \\ \tau\maps F(k)(x)\to x' &\textrm{in }F(m')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}}"']\ar[d,"{\begin{cases}g\maps b\to b' &\textrm{in }\A \\\chi_b\maps F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
 (a',\bot_{a'})\ar[r,"{\begin{cases}i'\maps a'\to m' &\textrm{in }\A \\!\maps F(i')(\bot_{a'})\to x' &\textrm{in }F(m')\end{cases}}"'] \& (m',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\maps b'\to m' &\textrm{in }\A \\!\maps F(o')(\bot_{b'})\to x' &\textrm{in }F(m')\end{cases}}"]
 \end{tikzcd}
\end{equation}
where the outside vertical legs come from the definition of $L$ on arrows \cref{eq:Lonarrows}. 
Explicitly, the above square commutativities translate to the conditions $k\circ i=i'\circ f$ and $k\circ o=o'\circ g$ in $\A$, and also to
\begin{gather}\label{eq:Grothcommutativity}
 F(k\circ i)(\bot_a)\cong Fk(Fi(\bot_a))\xrightarrow{Fk(!)}Fk(x)\xrightarrow{\tau}x'= \\
 F(i'\circ f)(\bot_a)\cong Fi'(Ff(\bot_a))\xrightarrow{Fi'(\chi_a)}Fi'(\bot_{a'})\xrightarrow{!}x'\nonumber
\end{gather}
in the fibre category $F(m')$, by composition in the Grothendieck category \cref{eq:compGrothcat}. Since both morphisms emanate from the mapped initial object in $F(m')$ under the finitely cocontinuous reindexing functors, they are the unique such into $x'$ therefore this gives no extra conditions; similarly for the equality including $o,o'$.

@@

@@

\subsection{Double categories}\label{sec:doublecats}
%%% Christina: Kenny, would you mind cleaning this section up to? I don't believe we need the full fledged definitions here by the way.
%%% Kenny: Sure!

Before formally defining `pseudo double category', it is helpful to have the following picture in mind. A pseudo double category $\lA$ has 2-morphisms shaped like:

\[
\begin{tikzpicture}[scale=1]
\node (D) at (-4,0.5) {$A$};
\node (E) at (-2,0.5) {$B$};
\node (F) at (-4,-1) {$C$};
\node (A) at (-2,-1) {$D$};
\node (B) at (-3,-0.25) {$\Downarrow a$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above]{$M$}(E)
(E) edge node [right]{$g$}(A)
(D) edge node [left]{$f$}(F)
(F) edge node [above]{$N$} (A);
\end{tikzpicture}
\]
We call $A, B, C$ and $D$ \define{objects}, $f$ and $g$ \define{vertical 1-morphisms}, $M$ and $N$ \define{horizontal 1-cells} and $a$ a \define{2-morphism}. 
%Note that a vertical 1-morphism is a morphism between 0-cells and a 2-morphism is a morphism between horizontal 1-cells. 
%We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'???   Or should we put a ``tick'' in here?
A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}. We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively. Thus $_f \lA_g(M,N)$ denotes the set of 2-morphisms in $\lA$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
%We follow the notation of Shulman \cite{Shulman2008} with the following definitions.

\begin{defn}\label{defn:double_category}
A \define{(pseudo) double category} $\lA$ is a category object internal to the 2-category $\Cat$.
\end{defn}

@@

\end{center}
such that $S(\alpha), S(\lambda), S(\rho), T(\alpha), T(\lambda)$ and $T(\rho)$ are all identities and that the coherence axioms of a monoidal category are satisfied. Following the notation of Shulman, objects of $\lD_0$ are called \define{objects}
%%% I'm tempted to delete 0-cells since we never use that term anywhere in any paper, but I do like the idea that "n+1 morphisms go between n cells".
%%% Christina: I am up for deletion of 0-cells
%%% Kenny: Okay, I deleted it.
and morphisms of $\lD_0$ are called \define{vertical 1-morphisms}. Objects of $\lD_1$ are called \define{horizontal 1-cells} and morphisms of $\lD_1$ are called \define{2-morphisms}. The morphisms of $\lD_0$, which are vertical 1-morphisms, will be denoted $f \maps A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \maps A \to B$. Then a 2-morphism $a \maps M \to N$ of $\lD_1$ with $S(a)=f,T(a)=g$ would look like:
\[
\begin{tikzpicture}[scale=1]
\node (D) at (-4,0.5) {$A$};
\node (E) at (-2,0.5) {$B$};
\node (F) at (-4,-1) {$C$};
\node (A) at (-2,-1) {$D$};
\node (B) at (-3,-0.25) {$\Downarrow a$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above]{$M$}(E)
(E) edge node [right]{$g$}(A)
(D) edge node [left]{$f$}(F)
(F) edge node [above]{$N$} (A);
\end{tikzpicture}
\]
\end{defn}
%A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}. We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively. Thus $_f \lA_g(M,N)$ denotes the set of 2-morphisms in $\lA$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.

@@

%\begin{defn}
%Let $\lD$ be a pseudo double category. Then the $\textbf{horizontal bicategory}$ of $\lD$, which we denote as $H(\lD)$, is the bicategory consisting of objects of $\lD$, morphisms that are horizontal 1-cells of $\lD$ and 2-morphisms that are globular 2-morphisms of $\lD$.
%\end{defn}
\begin{defn}\label{def:doublefun}
Given double categories $\lA$ and $\lX$, a \define{(pseudo) double functor} $\lF \colon\lA \to \lX$ consists of:
\begin{enumerate}
\item{functors $\lF_0 \colon \lA_0 \to \lX_0$ and $\lF_1 \colon \lA_1 \to \lX_1$ such that $S \lF_1 = \lF_0 S$ and $T \lF_1 = \lF_0 T$, and}
\item{for every composable pair of horizontal 1-cells $M$ and $N$ in $\lA$, a natural transformation $\phi_{M,N} \colon \lF(M) \odot \lF(N) \to \lF(M \odot N)$ called the \define{composite comparison} and for every object $a$ in $\lA$, a natural transformation $\phi_a \colon U_{\lF_0(a)} \to \lF_1(U_a)$ called the \define{unit comparison}. The components of each of these natural transformations are globular isomorphisms which satisfy the usual coherence axioms for a monoidal functor.}
\end{enumerate}
\end{defn}

\begin{defn}
Given double functors $(\lF,\phi),(\mathbb{G},\psi) \colon \lA \to \lX$, a \define{double transformation} $\alpha \colon \lF \Rightarrow \mathbb{G}$ consists of transformations $\alpha_0 \colon \lF_0 \Rightarrow \mathbb{G}_0$ and $\alpha_1 \colon \lF_1 \Rightarrow \mathbb{G}_1$ such that $S(\alpha_M) = \alpha_{S(M)}$ and $T(\alpha_M) = \alpha_{T(M)}$, and for two composable horizontal 1-cells $M$ and $N$ of $\lA$, $\alpha \circ \phi_{M,N} = \psi \circ (\alpha_M \odot \alpha_N)$ and $\alpha \circ \phi_a = \psi_a \circ \alpha$.
\end{defn}

\begin{comment}
\begin{defn}\label{def:doublefun}
Let $\lA$ and $\lB$ be double categories. A \define{(pseudo) double functor} is a functor $\lF \maps\lA\to \lB$ that takes items of $\lA$ to items of $\lB$ of the corresponding type, respecting vertical composition in the strict sense and the horizontal composition up to an assigned comparison $\phi$. This means that we have functors $\lF_0 \maps \lA_0 \to \lB_0$ and $\lF_1 \maps \lA_1 \to \lB_1$ such that the following equations are satisfied: 
\[   S \circ \lF_1 = \lF_0 \circ S, \qquad  T \circ \lF_1 = \lF_0 \circ T. \]
Sometimes for brevity we omit the subscripts and simply write $\lF$.

@@

 \[\xymatrix{
    (\lF(N_1) \odot \lF(N_{2})) \odot \lF(N_{3}) \ar[r]^{a'}\ar[d]_{\phi(N_1,N_{2}) \odot 1}
    & \lF(N_1) \odot (\lF(N_{2}) \odot \lF(N_{3})) \ar[d]^{1 \odot \phi(N_{2},N_{3})}\\
    \lF(N_1 \odot N_{2}) \odot \lF(N_{3}) \ar[d]_{\phi(N_1 \odot N_{2},N_{3})} &
    \lF(N_1) \odot \lF(N_{2} \odot N_{3}) \ar[d]^{\phi(N_1,N_{2} \odot N_{3})}\\
    \lF((N_1 \odot N_{2}) \odot N_{3})\ar[r]^{\lF(a)} &
    \lF(N_1 \odot (N_{2} \odot N_{3}))}\]
\end{enumerate}
We say the double functor $\lF$ is \define{strict} if the comparison constraints $\phi_a$ and $\phi_{N_1,N_2}$ are identities, \define{pseudo} if the comparison constraints are isomorphisms, and \define{oplax} if the comparison constraints go in the opposite direction.
\end{defn}
\end{comment}

@@

%Following the notation of Shulman \cite{Shulman2010}, given a double category $\lA$, we write $_f \lA_g(M,N)$ for the set of 2-morphisms in $\lA$ of the form:
%\[
% \xymatrix@-.5pc{
%   A \ar[r]|{|}^{M}  \ar[d]_f \ar@{}[dr]|{\Downarrow a}&
%    B\ar[d]^g\\
%    C \ar[r]|{|}_N & D
%  }
%\]

@@

\begin{thm}
Let $\lA$ and $\lX$ be symmetric monoidal double categories and let $\lF \maps \lA \to \lX$ be a symmetric monoidal pseudo double functor. If $\lF$ is part of a double equivalence, then $\lF$ is in fact part of a symmetric monoidal double equivalence, and $\lA$ and $\lX$ are equivalent as symmetric monoidal double categories.
\end{thm}

\begin{proof} Where is this proved???  \end{proof}
%%% Kenny: This isn't proved anywhere formally, as far as I know.

Let $\mathbf{Dbl}$ denote the 2-category of double categories, double functors and double transformations. One can check that $\mathbf{Dbl}$ has finite products, and in any 2-category with finite products we can define a `pseudomonoid' or a `weak' monoid, which is a categorified analogue of a monoid in which the left and right unitors and associators are not identities but natural isomorphisms. It is the 2-categorical structure of $\mathbf{Dbl}$, or more generally, any 2-category with finite limits, that enables us to do this. For example, a pseudomonoid in $\mathbf{Cat}$ is a monoidal category. We are primarily concerned with the (weak) monoidal double categories in which the associators and left and right unitors are natural isomorphisms.
\begin{defn}\label{defn:smdc}
A \define{monoidal double category} is a pseudomonoid internal to the monoidal 2-category $\mathbf{Dbl}$. Similarly, a \define{braided monoidal double category} is a braided pseudomonoid internal to $\mathbf{Dbl}$ and a \define{symmetric monoidal double category} is a symmetric pseudomonoid internal to $\mathbf{Dbl}$.
\end{defn}
For more details on the definition of (braided, symmetric) monoidal double category, we refer to Hansen and Shulman \cite{HS}.

@@

  A \textbf{monoidal double category} is a double category $\lA$ equipped with the following

@@

  Let $\lA$ be a double category and $f\maps A\to B$ a vertical

@@

	\end{tikzpicture}
	}
	%
	\raisebox{-0.5\height}{=}
	%
	\raisebox{-0.5\height}{
	\begin{tikzpicture}
	     \node (A0) at (0,2) {$A$};
	     \node (B0) at (1,2) {$A$};
		\node (C0) at (2,2) {$B$};
		\node (A) at (0,1) {$A$};
		\node (C) at (2,1) {$B$};
	%	\node (A') at (0,0) {$a$};
	%	\node (C') at (2,0) {$b$};
		%
		\path[->,font=\scriptsize,>=angle 90]
			(A0) edge node[above]{$U_A$} (B0)
			(B0) edge node[above]{$\hat{f}$} (C0)
			(A0) edge node[left]{$1$} (A)
			(C0) edge node[right]{$1$} (C)
		%	(A) edge node[left]{$1$} (A')
		%	(C) edge node[right]{$1$} (C')
			(A) edge node[below]{$\hat{f}$} (C);
		%	(A') edge node[below]{$\hat{f}$} (C');
		%
	%	\draw (0.5,.925) -- (0.5,1.075);
	%	\draw (0.5,-.075) -- (0.5,.075);
	%	\node () at (1,0.5) {\scriptsize{$\Downarrow 1$}};
		\node () at (1,1.4) {\scriptsize{$\Downarrow \rho_f$}};
	\end{tikzpicture}
	}
	\end{equation}
  A \textbf{conjoint} of $f$, denoted $\fchk \maps B\to A$, is a
  companion of $f$ in the double category $\lA^{h\cdot\mathrm{op}}$
  obtained by reversing the horizontal 1-cells, but not the vertical
  1-morphisms, of $\lA$.
\end{defn}
\noindent
%In a pseudo double category, the second equation above requires an insertion of unit isomorphisms to make sense due to horizontal composition only holding up to isomorphism.

@@

\begin{defn}\label{defn:monoidal_double_functor}
Given (braided, symmetric) monoidal double categories $\lA$ and $\lX$, a \define{(braided, symmetric) monoidal double functor} $\lF \colon \lA \to \lX$ is a double functor $\lF$ together with transformations $\theta \colon {\otimes \circ (\lF,\lF)} \to \lF \circ \otimes$ and $\theta_U \colon 1_\lX \to \lF \circ 1_\lA$ that satisfy the usual coherence axioms for a (braided, symmetric) monoidal functor with respect to $\otimes$.
\end{defn}

For more details on the definition of (braided, symmetric) monoidal functor, we refer to Hansen and Shulman \cite{HS}.
